\documentclass[titlepage]{article}


\usepackage{fancyhdr}
\usepackage{url}
\usepackage{tikz}
\usepackage{caption}

\pagestyle{fancy}

\fancyhead[L]{\thepage}



\title{Computer Workshop\\Assignment 3: {\LaTeX}}
\author{Dr. MalekiMajd}
\date{Due: 10 Azar, 1402}

\newcommand{\code}{\texttt}

\begin{document}
\maketitle

\section*{Assignment Notes:}
\begin{enumerate}
    \item Some questions may include material not yet covered in class. These questions are meant to help you develop your research skills.
    \item Cheating or copying homework is strictly forbidden. If caught, both students involved will receive a score of 0 on this assignment.
    \item If you have any questions, feel free to ask in the course's Telegram group to benefit your fellow classmates.
\end{enumerate}

\pagebreak

\section{Creating a document}
In this assignment, you have to recreate your \textit{Advanced Git assignment's} document. As you may have noticed,
The document was originally written in {\LaTeX} and it uses the elements discussed in the class.

However, there are a few twists to it and you have to pay attention to the details below:

\begin{enumerate}
    \item You are not required to draw the figures in the document. More details on this matter is discussed in the \textit{extra points} section.
    \item You have to include an image (any image you desire) at the end of your document. With the caption
        "This is just a test".
    \item Include a Table Of Contents (TOC) after the title page.
    \item Make sure to use the package \texttt{fancyhdr} to include headers and footers in your doucment.
    \item Make sure to pay attention to the formatting of the text in the original document.
\end{enumerate}

\section{Extra Points}
\begin{enumerate}
    \item Use the URL below to add the graphs in the figures:
        \url{https://www.baeldung.com/cs/latex-drawing-graphs}
\end{enumerate}

\paragraph{NOTE:}
Make sure to provide both the \texttt{.tex} file and the PDF file of it in the \texttt{ZIP}
file you want to upload to Quera.

\end{document}

