\documentclass[titlepage]{article}

\usepackage{fancyhdr}
\usepackage{xurl}


\title{Computer Workshop\\Assignment No. 5 --- GNU/Linux}
\author{Dr.\ MalekiMajd}
\date{Due 25 Dey, 1402}
\begin{document}
\maketitle

\section*{Notes on the assignment:}
\begin{enumerate}
        \item Questions might contain material that has not been taught in class.
        These questions are provided to help students learn how to find
        information on their own and improve their research skills.
    \item Cheating or copying homework will not be tolerated. If seen, both of
        the students will receive 0 points on that assignment.
    \item In case of any questions, mention your questions in the course's Telegram
        group to benefit others from your question.
\end{enumerate}

\pagebreak

\section{GNU}
Watch the video below and write 3 things that you learned from it:


\url{https://www.fsf.org/blogs/community/help-others-find-free-software-watch-and-share-escape-to-freedom}

\section{Kernel}
\begin{enumerate}
    \item Research on what the kernel generally is and what purpose it serves.
    \item Research on what a kernel module is and what purpose it serves.
\end{enumerate}

\section{Systemd}
\begin{enumerate}
    \item What purpose does it have in your operating system?
    \item Explain why some tend to criticize Systemd and for what reason? (Hint: Unix philosophy)
    \item Research on what systemd services are and what purpose they serve.
\end{enumerate}

\section{Graphics}
\begin{enumerate}
    \item Explain what a display server protocol is.
    \item Explain the difference between a desktop environment and a window manager.
    \item Mention some examples of window managers and desktop environments.
\end{enumerate}

\section{Ricing}
\begin{enumerate}
    \item Explain what the term “ricing” means in the GNU/Linux community.
    \item Find a picture of a rice that you liked the most. (Hint: try to search for a subreddit in Reddit that users post their rices there)
\end{enumerate}

\section{Suckless software}
\begin{enumerate}
    \item Briefly explain what Suckless software is.
    \item Briefly explain what philosophy is behind their software.
\end{enumerate}

\section{Shells}
\begin{enumerate}
    \item Explain what a POSIX-compliant shell is.
    \item For the following scenarios provide a useful command:
    \begin{enumerate}
        \item Write a command to find how many lines include the word “hello” in the files of a directory called “testDir”.
        \item Save the output of the command 'ls' in long format in a file called 'allthefiles.txt'.
        \item Write a command to find the number of files that have the type '.c' in a directory called “testDir”.
    \end{enumerate}
\end{enumerate}

\end{document}
