\documentclass[titlepage]{article}

\title{Computer Workshop\\Assignment No. 1 - Introduction}
\author{Dr. MalekiMajd}
\date{Due 16 Aban, 1402}

\begin{document}
\maketitle

\section*{Notes on the assignment:}
\begin{enumerate}
        \item Questions might contain material that has not been taught in class.
        These questions are provided to help students learn how to find
        information on their own and improve their research skills.
    \item Cheating or copying homework will not be tolerated. If seen, both of
        the students will receive 0 points on that assignment.
    \item In case of any questions, mention your questions in the course's Telegram
        group to benefit others from your question.
\end{enumerate}

\pagebreak

Explore the internet and research on the topics given below. Using the Vim extension
on Visual Studio Code is recommended for further experiment. For each of the topics,
write your understanding on that topic from your research.

\subsection{Basic navigation}
\begin{enumerate}
    \item Basic navigation (keys h, j, k, l)
    \item Navigating between text elements (keys w, W, e, E, b, B)
    \item keys G and gg.
    \item keys 0 and \$.
\end{enumerate}

\subsection{Modes}
\begin{enumerate}
    \item Explain the three modes available in Vim: Normal, Insert and Visual.
        Explain the usage of each mode in Vim.
    \item Explain how we can enter insert mode from normal mode. Mention at least
        two keys to enter insert mode.
    \item What key can we use while in insert mode to exit to normal mode?
\end{enumerate}

\subsection{Manipulating text}
\begin{enumerate}
    \item Explain what the key r does while in normal mode.
    \item Explain what the key x does while in normal mode.
    \item Explain what the keys dd do while in normal mode.
    \item Explain what the keys diw do while in normal mode.
\end{enumerate}



\subsection{Yanking/Copying}
\begin{enumerate}
    \item Explain what yanking is in Vim.
    \item Use the keys dd and then use the key p somewhere else (in normal mode), Explain what
        happens when typing each of these keys.
\end{enumerate}

\subsection{Searching for text}
\begin{enumerate}
    \item Explain searching using the / key in Vim.
\end{enumerate}

\section{Debugging}
\begin{enumerate}
    \item Debug the program discussed in the lecture slides or design a flawed code and explain the debugging process in detail.
    \item Attempt to debug a program that prints a string without a newline character (e.g., `printf("hello")`).
        Research and explain why the string doesn't appear in the console during debugging 
        and why it does when the string contains a newline character (`\textbackslash n`).
\end{enumerate}

\section{Basic Command Line}
\begin{enumerate}
    \item Explain the following PowerShell commands:
    \begin{enumerate}
        \item `cd` (Change Directory)
        \item `ls` (List)
        \item `pwd` (Print Working Directory)
        \item `mkdir` (Make Directory)
    \end{enumerate}
    \item Using PowerShell, perform the following tasks and take screenshots:
    \begin{enumerate}
        \item Get the current location using one of the mentioned commands.
        \item List all directories you are in and navigate to your user's Desktop directory.
        \item Once in your user's Desktop folder, create a directory called "cw4021iust."
        \item Enter the newly created directory and create two additional folders named "1" and "2."
        \item After creating the two new directories, list the directories in "cw4021iust" to ensure they were created correctly.
    \end{enumerate}
\end{enumerate}

\pagebreak

\section{Extra Points}
\subsection{Vim}
\begin{enumerate}
    \item Explain what macros are in Vim and provide examples on how to use them.
    \item Research about marks in vim and explain them in detail. Provide examples for their usages.
\end{enumerate}
\subsection{Debugging}
\begin{enumerate}
    \item Learn about the dbg-macro project in the sharkdp/dbg-macro GitHub repository and explain its
        features in complete detail. What advantages and disadvantages does it have compared to the
        debugging method discussed?
\end{enumerate}
\end{document}
